### 2025-05-16 appendices/haiti/appendixHaiti.Rnw
Adressing pre-defense review issue: Table B.2 exceeds past the 1" right side margin

\begin{figure}[ht]
<<m1Profs, fig.height=5, fig.width=6, echo=FALSE, warning=FALSE, message=FALSE>>=
# Create a mapping between department names and what should be shown in figures
h1_plots <- list()
for (i in 1:length(prof_params)) {
  p = prof_params[i]
  if (p == 'betat') {
    my_lab <- TeX('$\\zeta')
  } else if (grepl('^beta[[:digit:]]$', p)) {
    num <- gsub('^beta', '', p)
    my_lab <- TeX(paste0('$\\beta_', num, '$'))
  } else if (p == 'E_0') {
    my_lab <- TeX('$E_0(0)$')
  } else if (p == 'I_0') {
    my_lab <- TeX('$I_0(0)$')
  } else if (p == 'nu' || p == 'rho') {
    my_lab <- TeX(paste0('$\\', p, '$'))
  } else if (p == 'sig_sq_epi') {
    my_lab <- TeX('$\\sigma_{proc}$: Epidemic')
  } else if (p == 'sig_sq_end') {
    my_lab <- TeX('$\\sigma_{proc}$: Endemic')
  } else if (p == 'tau_end') {
    my_lab <- TeX('$\\log(\\psi)$: Endemic')
  } else if (p == 'tau_epi') {
    my_lab <- TeX('$\\log(\\psi)$: Epidemic')
  }

@@

\begin{table}[!h]
\centering
\caption[Model~1 parameter estimates and confidence intervals.]{\label{tab:mod1CI}Model~1 parameter estimates and their corresponding confidence intervals, obtained via the MCAP algorithm.}
\vspace{2mm}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Mechanism} & \textbf{Parameter} & \textbf{MLE} & $\bm{95\%}$ \textbf{Confidence Interval}
\\
\hline
\hline

@@

  Process noise {\small (wk\textsuperscript{1/2})} & $\sigmaProc: \mathrm{Epi}$ & $\Sexpr{myround(h1_mles %>% filter(prof_var == 'sig_sq_epi') %>% pull(value), 3)}$
   &
  $(\Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_epi') %>% pull(lower), 3)}, \Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_epi') %>% pull(upper), 3)})$
\\
\hline

  Process noise {\small (wk\textsuperscript{1/2})} & $\sigmaProc: \mathrm{End}$ & $\Sexpr{myround(h1_mles %>% filter(prof_var == 'sig_sq_end') %>% pull(value), 3)}$
   &
  $(\Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_end') %>% pull(lower), 3)}, \Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_end') %>% pull(upper), 3)})$
\\
\hline

@@

\begin{figure}[ht]
<<m2Profs, fig.height=3, fig.width=5, echo=FALSE, warning=FALSE, message=FALSE>>=
cowplot::plot_grid(
  plotlist = h2_plots, ncol = 3,
  align = 'h',
  rel_widths = c(1.15, 1, 1)
)
@
\caption[MCAP confidence intervals for Model 2 parameters.]{\label{fig:m2Profs}MCAP confidence intervals for Model 2 parameters. The vertical blue line indicates the MLE.}
\end{figure}

\begin{table}[!h]
\centering
\caption[Model~2 parameter estimates and confidence intervals.]{\label{tab:mod2CI}Model~2 parameter estimates and their corresponding confidence intervals, obtained via profile likelihood.}
\vspace{2mm}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Mechanism} & \textbf{Parameter} & \textbf{MLE} & $\bm{95\%}$ \textbf{Confidence Interval}
\\
\hline
\hline

@@

\begin{figure}[ht]
<<m3Profs, fig.height=4.6, fig.width=5.8, echo=FALSE, warning=FALSE, message=FALSE>>=
h3_plots <- list()
for (i in 1:length(prof_params)) {
  p = prof_params[i]
  if (p == 'mu_B') {
    my_lab <- TeX('$\\delta_W$')
  } else if (p == 'XthetaA') {
    my_lab <- TeX('$\\sqrt{\\epsilon_W}$')
  } else if (p == 'thetaI') {
    my_lab <- TeX('$\\mu_W$')
  } else if (p == 'lambdaR') {
    my_lab <- TeX('$a$')
  } else if (p == 'r') {
    my_lab <- TeX('$r$')
  } else if (p == 'std_W') {
    my_lab <- TeX('$\\sigma_{proc}$')
  } else if (p == 'epsilon') {
    my_lab <- TeX('$\\rho$')
  } else if (p == 'k') {
    my_lab <- TeX('$\\psi$')
  }

@@

\begin{table}[!h]
\centering
\caption[Model~3 parameter estimates and confidence intervals.]{\label{tab:mod3CI}Model~3 parameter estimates and their corresponding confidence intervals, obtained via the MCAP algorithm.}
\vspace{2mm}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Mechanism} & \textbf{Parameter} & \textbf{MLE} & $\bm{95\%}$ \textbf{Confidence Interval}
\\
\hline
\hline

 Process Noise {\small (wk\textsuperscript{1/2})} & $\sigmaProc$ & $\Sexpr{myround((h3_mles %>% filter(prof_var == 'std_W') %>% pull(value)) * sqrt(52), 3)}$
   &
  $(\Sexpr{myround((all_ci %>% filter(prof_var == 'std_W') %>% pull(lower)), 3)}, \Sexpr{myround((all_ci %>% filter(prof_var == 'std_W') %>% pull(upper)), 3)})$
\\
\hline

 Water Survival {\small (wk)} & $\Wremoval^{-1}$ & $\Sexpr{myround(52 / (h3_mles %>% filter(prof_var == 'mu_B') %>% pull(value)), 3)}$
   &
  $(\Sexpr{myround(1 / (all_ci %>% filter(prof_var == 'mu_B') %>% pull(upper)), 3)}, \Sexpr{myround(1 / (all_ci %>% filter(prof_var == 'mu_B') %>% pull(lower)), 3)})$
\\
\hline

 Human to Water Shedding {\small $\frac{\mathrm{km^2}}{\mathrm{wk}}$} & $\Wshed$ & $\Sexpr{signif((h3_mles %>% filter(prof_var == 'thetaI') %>% pull(value))/52, 3)}$
   &
  $(\Sexpr{signif(all_ci %>% filter(prof_var == 'thetaI') %>% pull(lower), 3)}, \Sexpr{signif(all_ci %>% filter(prof_var == 'thetaI') %>% pull(upper), 3)})$
\\
\hline

@@

\begin{figure}[!ht]
<<h3UnitLikes, fig.height=3, fig.width=5.5, echo=FALSE>>=
ggplot(bench_M3_joined, aes(x = ll, y = reorder(unit, ll))) +
  geom_point(aes(col = type)) +
  ylab("Unit") +
  xlab("Log Likelihood") +
  scale_color_manual(
    labels = c("ll" = "Benchmark", "ll_est" = "Model 3"),
    values = c("ll" = "#1b9e77", "ll_est" = "#d95f02")
  ) +
  theme(legend.title = element_blank(),
        axis.title.y = element_blank()) + 
  theme_bw()
@
\caption[Model~3 unit log-likelihoods.]{\label{fig:h3UnitLikes}Log-likelihoods of Model~3 for each department compared to the corresponding benchmark model prior to the inclusion of parameters that account for Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!ht]
<<finalUnitLLFig, fig.height=3, fig.width=5.5, echo=FALSE>>=
ggplot(bench_M3_joined_final, aes(x = ll, y = reorder(unit, ll))) +
  geom_point(aes(col = type)) +
  ylab("Unit") +
  xlab("Log Likelihood") +
  scale_color_manual(
    labels = c("ll" = "Benchmark", "ll_est" = "Model 3"),
    values = c("ll" = "#1b9e77", "ll_est" = "#d95f02")
  ) +
  theme(legend.title = element_blank(),
        axis.title.y = element_blank())
@
\caption{\label{fig:finalUnitLL}Log-likelihoods of Model~3 for each department compared to the corresponding benchmark model after adding and estimating parameters related to Hurricane Matthew.}
\end{figure}

>>>>

\begin{figure}[ht]
<<m1Profs, fig.height=5, fig.width=6, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'>>=
# Create a mapping between department names and what should be shown in figures
h1_plots <- list()
for (i in 1:length(prof_params)) {
  p = prof_params[i]
  if (p == 'betat') {
    my_lab <- TeX('$\\zeta')
  } else if (grepl('^beta[[:digit:]]$', p)) {
    num <- gsub('^beta', '', p)
    my_lab <- TeX(paste0('$\\beta_', num, '$'))
  } else if (p == 'E_0') {
    my_lab <- TeX('$E_0(0)$')
  } else if (p == 'I_0') {
    my_lab <- TeX('$I_0(0)$')
  } else if (p == 'nu' || p == 'rho') {
    my_lab <- TeX(paste0('$\\', p, '$'))
  } else if (p == 'sig_sq_epi') {
    my_lab <- TeX('$\\sigma_{proc}$: Epidemic')
  } else if (p == 'sig_sq_end') {
    my_lab <- TeX('$\\sigma_{proc}$: Endemic')
  } else if (p == 'tau_end') {
    my_lab <- TeX('$\\log(\\psi)$: Endemic')
  } else if (p == 'tau_epi') {
    my_lab <- TeX('$\\log(\\psi)$: Epidemic')
  }

@@

\begin{table}[!h]
\centering
\caption[Model~1 parameter estimates and confidence intervals.]{\label{tab:mod1CI}Model~1 parameter estimates and their corresponding confidence intervals, obtained via the MCAP algorithm.}
\vspace{2mm}
\begin{tabular}{|L{3.60cm}|C{2.1cm}|C{1.9cm}|C{3.95cm}|}
\hline
\centering \textbf{Mechanism} & \textbf{Parameter} & \textbf{MLE} & $\bm{95\%}$ \textbf{Confidence Interval} \\
\hline
\hline

@@

  Process noise {\footnotesize (wk\textsuperscript{1/2})} & $\sigmaProc: \mathrm{Epi}$ & $\Sexpr{myround(h1_mles %>% filter(prof_var == 'sig_sq_epi') %>% pull(value), 3)}$
   &
  $(\Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_epi') %>% pull(lower), 3)}, \Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_epi') %>% pull(upper), 3)})$
\\
\hline

  Process noise {\footnotesize (wk\textsuperscript{1/2})} & $\sigmaProc: \mathrm{End}$ & $\Sexpr{myround(h1_mles %>% filter(prof_var == 'sig_sq_end') %>% pull(value), 3)}$
   &
  $(\Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_end') %>% pull(lower), 3)}, \Sexpr{myround(all_ci %>% filter(prof_var == 'sig_sq_end') %>% pull(upper), 3)})$
\\
\hline

@@

\begin{figure}[ht]
<<m2Profs, fig.height=3, fig.width=5.5, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'>>=
cowplot::plot_grid(
  plotlist = h2_plots, ncol = 3,
  align = 'h',
  rel_widths = c(1.15, 1, 1)
)
@
\caption[MCAP confidence intervals for Model 2 parameters.]{\label{fig:m2Profs}MCAP confidence intervals for Model 2 parameters. The vertical blue line indicates the MLE.}
\end{figure}

\begin{table}[!h]
\centering
\caption[Model~2 parameter estimates and confidence intervals.]{\label{tab:mod2CI}Model~2 parameter estimates and their corresponding confidence intervals, obtained via profile likelihood.}
\vspace{2mm}
\begin{tabular}{|L{3.25cm}|C{2.1cm}|C{1.9cm}|C{4.2cm}|}
\hline
\centering \textbf{Mechanism} & \textbf{Parameter} & \textbf{MLE} & $\bm{95\%}$ \textbf{Confidence Interval} \\
\hline
\hline

@@

\begin{figure}[ht]
<<m3Profs, fig.height=4.6, fig.width=5.8, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'>>=
h3_plots <- list()
for (i in 1:length(prof_params)) {
  p = prof_params[i]
  if (p == 'mu_B') {
    my_lab <- TeX('$\\delta_W$')
  } else if (p == 'XthetaA') {
    my_lab <- TeX('$\\sqrt{\\epsilon_W}$')
  } else if (p == 'thetaI') {
    my_lab <- TeX('$\\mu_W$')
  } else if (p == 'lambdaR') {
    my_lab <- TeX('$a$')
  } else if (p == 'r') {
    my_lab <- TeX('$r$')
  } else if (p == 'std_W') {
    my_lab <- TeX('$\\sigma_{proc}$')
  } else if (p == 'epsilon') {
    my_lab <- TeX('$\\rho$')
  } else if (p == 'k') {
    my_lab <- TeX('$\\psi$')
  }

@@

\begin{table}[!h]
\centering
\caption[Model~3 parameter estimates and confidence intervals.]{\label{tab:mod3CI}Model~3 parameter estimates and their corresponding confidence intervals, obtained via the MCAP algorithm.}
\vspace{2mm}
\begin{tabular}{|L{3.60cm}|C{2.1cm}|C{1.9cm}|C{4.3cm}|}
\hline
\centering \textbf{Mechanism} & \textbf{Parameter} & \textbf{MLE} & $\bm{95\%}$ \textbf{Confidence Interval} \\
\hline
\hline

 Process Noise {\footnotesize (wk\textsuperscript{1/2})} & $\sigmaProc$ & $\Sexpr{myround((h3_mles %>% filter(prof_var == 'std_W') %>% pull(value)) * sqrt(52), 3)}$
   &
  $(\Sexpr{myround((all_ci %>% filter(prof_var == 'std_W') %>% pull(lower)), 3)}, \Sexpr{myround((all_ci %>% filter(prof_var == 'std_W') %>% pull(upper)), 3)})$
\\
\hline

 Water Survival {\footnotesize (wk)} & $\Wremoval^{-1}$ & $\Sexpr{myround(52 / (h3_mles %>% filter(prof_var == 'mu_B') %>% pull(value)), 3)}$
   &
  $(\Sexpr{myround(1 / (all_ci %>% filter(prof_var == 'mu_B') %>% pull(upper)), 3)}, \Sexpr{myround(1 / (all_ci %>% filter(prof_var == 'mu_B') %>% pull(lower)), 3)})$
\\
\hline

 Human to Water Shedding {\footnotesize $\frac{\mathrm{km^2}}{\mathrm{wk}}$} & $\Wshed$ & $\Sexpr{signif((h3_mles %>% filter(prof_var == 'thetaI') %>% pull(value))/52, 3)}$
   &
  $(\Sexpr{signif(all_ci %>% filter(prof_var == 'thetaI') %>% pull(lower), 3)}, \Sexpr{signif(all_ci %>% filter(prof_var == 'thetaI') %>% pull(upper), 3)})$
\\
\hline

@@

\begin{figure}[!ht]
<<h3UnitLikes, fig.height=3, fig.width=5.5, echo=FALSE,fig.align='center'>>=
ggplot(bench_M3_joined, aes(x = ll, y = reorder(unit, ll))) +
  geom_point(aes(col = type)) +
  ylab("Unit") +
  xlab("Log Likelihood") +
  scale_color_manual(
    labels = c("ll" = "Benchmark", "ll_est" = "Model 3"),
    values = c("ll" = "#1b9e77", "ll_est" = "#d95f02")
  ) +
  theme(legend.title = element_blank(),
        axis.title.y = element_blank()) + 
  theme_bw()
@
\caption[Model~3 unit log-likelihoods.]{\label{fig:h3UnitLikes}Log-likelihoods of Model~3 for each department compared to the corresponding benchmark model prior to the inclusion of parameters that account for Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!ht]
<<finalUnitLLFig, fig.height=3, fig.width=5.5, echo=FALSE, fig.align='center'>>=
ggplot(bench_M3_joined_final, aes(x = ll, y = reorder(unit, ll))) +
  geom_point(aes(col = type)) +
  ylab("Unit") +
  xlab("Log Likelihood") +
  scale_color_manual(
    labels = c("ll" = "Benchmark", "ll_est" = "Model 3"),
    values = c("ll" = "#1b9e77", "ll_est" = "#d95f02")
  ) +
  theme(legend.title = element_blank(),
        axis.title.y = element_blank())
@
\caption{\label{fig:finalUnitLL}Log-likelihoods of Model~3 for each department compared to the corresponding benchmark model after adding and estimating parameters related to Hurricane Matthew.}
\end{figure}
